Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning

### 2013-12-12 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
duplicate from

\section{Introduction}
The aim of this work is verification hypothesis of patterns extraction possibility from from time series, which could be classified as providing better statistic and more accurate prognosis. Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period after the time which pattern was learn in. This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}. Research intention was also to follow reproducibility principle of other researchers studies, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\

>>>>

\section{Introduction}
The aim of this work is verification hypothesis of patterns extraction possibility from time series, which could be classified as providing better statistic and more accurate prognosis. Another important objective is confirmation of assumption, that financial markets time series have a “memory” of pattern efficiency in a time period after the time which pattern was learn in. This approach is consistent with the classic aim of machine learning shown by K.Murphy’ego \cite{Murphy}, especially to financial markets described by Satchwell \cite{Satchwell}. Research intention was also to follow reproducibility principle of other researchers studies, as well as by themselves, in other data environments, to make sense of the use of computational intelligence in its reasonable reproducibility \cite{Polya, Donoho}, in extracting of the regularity from chaos \cite{Ball, Pedrycz}.\\
